Towards a standardized evaluation of multiple imputation routines

### 2022-01-25 Manuscript/StandardizedEvaluation.Rmd
Outline simulation function

```{r mis_mech, echo=FALSE, fig.cap="\\label{fig:mis_mech}Three missingness mechanisms that yield approximately 50 percent missingness ($N=500$). Displayed are a MCAR mechanism, a right-tailed MAR mechanism generated from bivariate normal data with correlation $\rho=.8$ and the same MAR mechanism, now generated from bivariate normal data with correlation $\rho= 0$."}
knitr::include_graphics("img/plot_mmech.pdf")
```

@@

> We generated missing data following a MAR missingness mechanism.

>>>>

```{r mis_mech, echo=FALSE, fig.cap="\\label{fig:mis_mech}Three missingness mechanisms that yield approximately 50 percent missingness ($N=500$). Displayed are a MCAR mechanism, a right-tailed MAR mechanism generated from bivariate normal data with correlation $\\rho=.8$ and the same MAR mechanism, now generated from bivariate normal data with correlation $\\rho= 0$."}
knitr::include_graphics("img/plot_mmech.pdf")
```

@@

> *We generated missing data following a MAR missingness mechanism.*
